\subsection{Operation Model for oeSetCrisisHandler}

\label{OM-oeSetCrisisHandler}


The \msrcode{oeSetCrisisHandler} operation has the following properties:

	\begin{operationmodel}
	\addheading{Operation}
	\adddoublerow{oeSetCrisisHandler}{sent to declare himself as been the handler of a crisis having the specified id.}

	\addrowheading{Parameters}
	\addnumbereddoublerow{}{AdtCrisisID: dtCrisisID}{the identification information used to determine the crisis} 
	\addnumbereddoublerow{}{AdtCrisisID: dtCrisisID}{ } 

	\addrowheading{Return type}
	\addsinglerow{ptBoolean}

	\addrowheading{Pre-Condition (protocol)}
	\addnumberedsinglerow{PreP}{the system is started}
	\addnumberedsinglerow{PreP}{the actor logged previously and did not log out ! (i.e. the associated ctCoordinator instance is considered logged)}
		
	\addrowheading{Pre-Condition (functional)}
	\addnumberedsinglerow{PreF}{ there exist one crisis having the given id in the pre-state.}

	\addrowheading{Post-Condition (functional)}
	\addnumberedsinglerow{PostF}{the ctCrisis instance having the provided id is in handled status at poststate and
	is associated to the actor that sends the message
	(which himself is notified with a textual message as confirmation).}
	\addnumberedsinglerow{PostF}{All the alerts related to this crisis are sent to the actor such that he can
	 decide how to handle them.}
	\addnumberedsinglerow{PostF}{if the crisis was already handled at pre-sate then the associated handler actor is 
	notified about the change of handler for one of his crisis 
	(n.b. it might be the same even if not relevant).}
	\addnumberedsinglerow{PostF}{a message is sent to the communication company for any human related to an alert 
	associated to the crisis. A human will receive as many messages as alerts he sent 
	despite the fact that they might relate to the same crisis (i.e. one alert, one acknoledgement).}

	\addrowheading{Post-Condition (protocol)}
	\addnumberedsinglerow{PostP}{ none}
	\end{operationmodel}



	% ------------------------------------------
	% MCL Listing
	% ------------------------------------------
	\vspace{1cm}
	The listing~\ref{OM-actCoordinator-oeSetCrisisHandler-MCL-LST} provides the \msrmessir (MCL-oriented) specification of the operation.
	
	\scriptsize
	\vspace{0.5cm}
	\begin{lstlisting}[style=MessirStyle,firstnumber=auto,captionpos=b,caption={\msrmessir (MCL-oriented) specification of the operation \emph{oeSetCrisisHandler}.},label=OM-actCoordinator-oeSetCrisisHandler-MCL-LST]

	/* Pre Protocol:*/ 
	preP{let theSystem: ctState in
	  		let theActor:actAuthenticated in
	  		self.rnActor.rnSystem = TheSystem
	  		and self.rnActor = TheActor
	  
			/* PreP01 */
	  		and TheSystem.vpStarted = true
			/* PreP02 */
	  		and TheActor.rnctAuthenticated.vpIsLogged = true}
	
	/* Pre Functional:*/
	preF{let TheSystem: ctState in
			self.rnActor.rnSystem = TheSystem
			and TheSystem.rnctCrisis->exists(a: ctCrisis | a.id = AdtCrisisID)}
	
	/* Post Functional:*/ 
	postF{let TheSystem: ctState in
			let TheCrisis: ctCrisis in
			let TheActor: actCoordinator in
			let TheOldActor: actCoordinator in
			let TheAlerts: Set(ctAlert) in
			let  TheactComCompany:actComCompany in
			TheSystem = self.rnActor.rnSystem
			and TheactComCompany = TheSystem.rnactComCompany
			and TheActor = self.rnActor
			and TheCrisis = TheSystem.rnctCrisis->any(a: ctCrisis | a.id = AdtCrisisID)
			and TheCrisis@post.status = 'handled'
			and TheCrisis@post.rnHandler = TheActor.rnctCoordinator
			
			and if (TheCrisis.status = 'handled')
				then (TheOldActor = TheCrisis.rnHandler
					and TheOldActor.rnInterfaceIN^ieChangeHandlerCrisis(AdtCrisisID)
				)
				else (true)
				endif
			and TheAlerts = TheCrisis.rnAlert
			and TheAlerts->forAll(a:ctAlert | if (a.hash = a.hash.calculate()) 
													  then (a@post = a) 
													  else (let c:ctAlertBackup in
															c = TheAlertsBackup->select(b:ctAlertBackup | a.id = b.id)
															and a@post = c) 
													  endif)
			and TheAlerts->forAll(a: ctAlert | let AHuman: ctHuman in
											   let AdtSms: dtSMS in
											   AdtSms = 'The Coordinator of the crisis related to your Alert change'
											   AHuman = a.rnSignaler
											   and TheactComCompany.rnInterfaceIN^ieSmsSend(AHuman.id, AdtSms)
			)}
	
	/* Post Protocol:*/ 
	postP{ }
	
	\end{lstlisting}
	\normalsize 
	
	
	
	





